Decomposition-based Job-shop Scheduling with Constrained Clustering

### 2021-10-14 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
put together modifications in Section 3

Methods suggested in the previous work \cite{koonce2000using, harrath2002genetic, shahzad2010discovering, ismail2012production, adibi2014clustering, nasiri2019data} used characterizations of scheduling instances based on the following features: priority, processing time, remaining processing time, machine load, and route position. 
Most of the approaches converted the quantitative values of the attributes into qualitative data. As mentioned in these studies, the main reason for this conversion was to make the heuristic dispatching rules more generic and allow their application to several scheduling problems. 
In this work, we suggest a method that can work directly on the sets of features and does not require any problem-specific transformations. However, our clustering method for JSP instance decomposition requires all features to have numerical values allowing distance measures to estimate similarities/dissimilarities between operations of jobs.

\begin{table}[tb]
  \setlength{\tabcolsep}{10.0pt}
  \centering
    \begin{center}
    \caption{Features extracted for the sample problem instance.}
    \label{tab3}
   %\begin{adjustwidth}{0.0cm}{}
      \begin{tabular}{c  c  c  c  c  c}
        \textbf{Operation} & \textbf{RPT} & \textbf{EST} & \textbf{ML} & \textbf{\stfifo} & \textbf{\wtfifo}\\
        \hline
                      \\
        $O_{1,1}$  & 17 & 0   & 20	&  0  & 0\\
        $O_{1,2}$  & 8  & 9   & 3		&  9  & 0\\
        $O_{1,3}$  & 5  & 12  & 5	  &  12 & 0\\
                      \\
        $O_{2,1}$  & 12 & 0   & 10	&  0  & 0\\
        $O_{2,2}$  & 8  & 4   & 11	&  9  & 5\\
        $O_{2,3}$  & 2  & 10  & 7	  &  17 & 2\\
                          \\
        $O_{3,1}$  & 12 & 0  & 11	  &  0  & 0\\
        $O_{3,2}$  & 8  & 4  & 6		&  4  & 0\\
        $O_{3,3}$  & 5  & 7  & 5		&  15 & 8\\
      \end{tabular}
  %\end{adjustwidth}
    \end{center} 
  \end{table}

In our approach we evaluated the following features:
\begin{description}
  \item[Processing Time (PT)] that represents the execution time of a particular operation in a machine. This feature is provided in every JSP instance, like in the sample instance presented in Table \ref{tab1}.

@@

  \item[Waiting Time (WT)] is also a set of features, like ST, for which computation we used the same greedy algorithm as above with three different heuristics EST (\wtest), FIFO (\wtfifo), and MTWR (\wtmtwr). Each feature in \textit{WT} set is the difference between the scheduled starting time of a particular operation and the ending time of its predecessor.
  As shown in Table~\ref{tab3}, the waiting time of $O_{2,2}$ is $5$ since the processing of its predecessor $O_{2,1}$ finishes at time $4$ and FIFO heuristic selects $O_{2,2}$ for scheduling to machine $2$ at time $9$, just as in the \stfifo case.
\end{description}
%
All features extracted from a given JSP instance are provided to our decomposition method presented in the following section.

\section{Method}
\label{sec:method}
%In this section, we will show the implementation of our proposed model and how it works. 
The proposed method comprises two main steps: 
\begin{enumerate*}[label=\emph{(\roman*)}]
  \item first, it decomposes a problem into a sequence of sub-problems, called \emph{time windows}; 
  \item second, the sub-problems are solved one after another such that each subsequent sub-problem gets solutions of the previous sub-problems as input.
\end{enumerate*}
As a result, the solution of the last sub-problem provides a complete schedule for the given JSP instance.
The computational efficiency of the approach and the quality of obtained schedules depend highly on the quality of decomposition obtained in the first step \cite{zhang2010hybrid,zhai2014decomposition}. 
%To address this problem, several decomposition approaches have been presented during the last decades \cite{zhai2014decomposition,singer2001decomposition,ovacik2012decomposition,uzsoy2000performance}.
Our approach uses a novel constraint clustering method to find a favorable decomposition of JSP instances using features of operations provided in them. Each cluster represents a time window, i.e., a subset of all operations that a scheduling algorithm must consider for the assignment.

>>>>

Methods suggested in the literature \cite{koonce2000using, harrath2002genetic, shahzad2010discovering, ismail2012production, adibi2014clustering, nasiri2019data} characterize instances of scheduling problems based on the following features: priority, processing time, remaining processing time, machine load, and sequence position. 
Most of these approaches convert the quantitative feature values % of the attributes
into qualitative attributes in order to obtain generic dispatching rules
that remain applicable to instances of different size.
% As mentioned in these studies, the main reason for this conversion was to make the heuristic dispatching rules more generic and allow their application to several scheduling problems. 
In this work, we propose a method that can be applied to feature values directly and does not require any problem-specific transformations. However, our clustering method for JSP instance decomposition requires all features to have numerical values, which permit the calculation of distance measures for estimating (dis)similarities between operations.

\begin{table}[tb]
  \setlength{\tabcolsep}{10.0pt}
  \centering
    \begin{center}
    \caption{Features extracted from the sample problem instance in Table~\ref{tab1}.}
    \label{tab3}
   %\begin{adjustwidth}{0.0cm}{}
      \begin{tabular}{c  c  c  c  c  c}
        \textbf{Operation} & \textbf{RPT} & \textbf{EST} & \textbf{ML} & \textbf{\stfifo} & \textbf{\wtfifo}\\
        \hline
                      \\
        $O_{1,1}$  & 17 & 0   & 20	&  0  & 0\\
        $O_{1,2}$  & 8  & 9   & 3		&  9  & 0\\
        $O_{1,3}$  & 5  & 12  & 5	  &  12 & 0\\
                      \\
        $O_{2,1}$  & 12 & 0   & 10	&  0  & 0\\
        $O_{2,2}$  & 8  & 4   & 11	&  9  & 5\\
        $O_{2,3}$  & 2  & 10  & 7	  &  17 & 2\\
                          \\
        $O_{3,1}$  & 12 & 0  & 11	  &  0  & 0\\
        $O_{3,2}$  & 8  & 4  & 6		&  4  & 0\\
        $O_{3,3}$  & 5  & 7  & 5		&  15 & 8\\
      \end{tabular}
  %\end{adjustwidth}
    \end{center} 
  \end{table}
%
% In our approach we evaluated the following features:
In detail, we consider the following features of jobs, operations, and machines:
\begin{description}
  \item[Processing Time (PT)] that represents the execution time of a particular operation in a machine. This feature is provided in every JSP instance, like in the sample instance presented in Table \ref{tab1}.

@@

  \item[Waiting Time (WT)] is also a set of features, like ST, for which computation we used the same greedy algorithm as above with three different heuristics EST (\wtest), FIFO (\wtfifo), and MTWR (\wtmtwr). Each feature in \textit{WT} set is the difference between the scheduled starting time of a particular operation and the ending time of its predecessor.
  As shown in Table~\ref{tab3}, the waiting time of $O_{2,2}$ is $5$ since the processing of its predecessor $O_{2,1}$ finishes at time $4$ and FIFO heuristic selects $O_{2,2}$ for scheduling to machine $2$ at time $9$, just as in the \stfifo case.
\end{description}
%
All features extracted from a given JSP instance are provided to our decomposition method presented in the next section.

\section{Constrained Clustering Algorithm}
\label{sec:method}
%In this section, we will show the implementation of our proposed model and how it works. 
The proposed method comprises two main steps: 
\begin{enumerate*}[label=\emph{(\roman*)}]
  \item first, it decomposes a problem into a sequence of sub-problems, called \emph{time windows}; 
  \item second, the sub-problems are solved one after another such that each subsequent sub-problem gets solutions of the previous sub-problems as input.
\end{enumerate*}
As a result, the solution of the last sub-problem provides a complete schedule for the given JSP instance.
The computational efficiency of the approach and the quality of obtained schedules depend highly on the quality of decomposition obtained in the first step \cite{zhang2010hybrid,zhai2014decomposition}. 
%To address this problem, several decomposition approaches have been presented during the last decades \cite{zhai2014decomposition,singer2001decomposition,ovacik2012decomposition,uzsoy2000performance}.
Our approach uses a novel constraint clustering method to find a favorable decomposition of JSP instances using features of operations provided in them. Each cluster represents a time window, i.e., a subset of all operations that a scheduling algorithm must consider for the assignment.
